---
title: "A New Tutorial"
tutorial:
  id: "setIDHereForAnswerRecording"
  version: 1.0
output:
  learnr::tutorial:
    css: css/style.css
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE,fig.align = 'center')
# Installed tutorials can not use functions stored in the R directory
# like a regular R package. Instead they need to be distributed and 
# sourced with each tutorial.
# See R/main.R for code to copy the folder/directory to each tutorial
source('./www/helper.R')

# #---------------------------------------------
# # Instructions for storing answers to the tutorials, not particularly useful for packaged tutorials
# record_answers <- function(tutorial_id, tutorial_version, user_id, event, data) {
#     cat(file=paste0(getwd(),'/answers.txt'),append=T,
#         as.numeric(Sys.time()), ".", 
#         tutorial_id, ".", tutorial_version, ": ", 
#         user_id, ", ", 
#         event, ", ", 
#         data$label, ", ", 
#         data$answer, ", ", 
#         data$correct, "\n", sep = "")
# }
# options(tutorial.event_recorder = record_answers)
# #---------------------------------------------
```


<!-- A Note on Printing Lecture and Tutorials:
Only those topics/elements that have been 'visited' will 
be printed. So if you haven't altered the UI then output
connected to that input won't be printed. To properly 
print to pdf, you need to have the css code below
Then: Run the document, Open in Browser and adjust all UI elements
Finally Ctrl+P from within the browser
-->
```{css print-tutorial-functionality}
@media print {
  @page {size: landscape}
  h2 {
        page-break-before: always;
  }
  .topicsContainer,
  .topicActions,
  .exerciseActions .skip {
    display: none;
  }
  .topics .tutorialTitle,
  .topics .section.level2,
  .topics .section.level3:not(.hide) {
    display: block;
  }
  .topics {
    width: 100%;
  }
  .tutorial-exercise, .tutorial-question {
    page-break-inside: avoid;
  }
  .section.level3.done h3 {
    padding-left: 0;
    background-image: none;
  }
  .topics .showSkip .exerciseActions::before {
    content: "Topic not yet completed...";
    font-style: italic;
  }
}

```
## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some pre-populated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```
