---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Package Information

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ExampleTutorial)](https://CRAN.R-project.org/package=ExampleTutorial)
<!-- badges: end -->

An example package for tutorials delivered through R

## Folder Structure

Tutorials are stored in the inst/tutorials directory. The emptyTutorial directory can be copied and ammended to create a new tutorial.

## Installation

Students can install the current version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Avery-Lisa/LearnRTutorial")
```

## Example

List all the tutorials in the package

```{r}
#intall.packages('learnr')
learnr::available_tutorials(package = 'LearnRTutorial')
```

This is how the tutorials are run from within RStudio 

```{r example, eval=F}
library(LearnRTutorial)
learnr::run_tutorial("LecturingWithLearnR", "LearnRTutorial")

```


